---
title: "Life Expectancy"
description: |
  An animated model to view a country's life expectancy.
output: distill::distill_article
---

[Life Expectancy](https://ourworldindata.org/life-expectancy) in a particular country is the number of years somebody can expect to live on average when born there. This is a popular metric for determining how healthy a country is. The plot below analyzes whether the Life Expectancy of a Country is effected by its GDP Per Capita using animation by Year.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(gganimate)
library(tidyverse)
library(gapminder)
library(plotly)
library(ggthemes)
library(viridis)
library(scales)
theme_set(theme_bw())
# gapminder
```

## Country Life Expectancy vs GDP Per Capita 
##### As a country's GDP per Capita increases, the Life Expectancy does as well

```{r, warning = FALSE}
x <- gapminder |>
  ggplot(aes(x = gdpPercap, y = lifeExp, color = continent, size = pop)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "lightblue") +
  scale_x_log10(labels = label_comma()) +
  scale_y_continuous(labels = label_comma()) +
  labs(x = "GDP Per Capita",
       y = "Life Expectancy",
       color = "Continent")
  x + transition_time(year) +
    labs(title = "Year: {frame_time}") +
    guides(size = FALSE)
```






