---
title: "Predictions"
description: |
  Models which are used to analyze countries.
date: "`r Sys.Date()`"
output: distill::distill_article
---

The models below use [Decision Trees](https://en.wikipedia.org/wiki/Decision_tree) which are tree-like models which are used to predict the chances that a certain event happens. Below I've created two decision trees which predict whether a country is considered wealthy or populous depending on the given factors. The number 1 is considered TRUE and the number 0 is considered false. (Ex: USA = 1 means that it is considered wealthy) 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rpart)
library(rpart.plot)
library(tidyverse)
library(gapminder)
library(repr)
```

## GDP Per Capita Decision Tree
##### The decision tree below predicts whether a country is considered rich based off of factors such as its population and continent.

```{r}
clean <- gapminder |>
  filter(year == 2007) |>
  mutate(rich = if_else(gdpPercap >= 25000, 1, 0))

tree <- rpart(formula = rich ~ pop + continent, data = clean, method = "class")

rpart.plot(tree)
```

## Population Decision Tree
##### This decision tree analyzes how populated a country is based off of its GDP per Capita, Life Expectancy, and Continent.
```{r}
clean2 <- gapminder |>
  filter(year == 2007) |>
  mutate(populated = if_else(pop > 50000000, 1, 0))

tree2 <- rpart(formula = populated ~ continent + lifeExp + gdpPercap, data = clean2, method = "class")
rpart.plot(tree2)
```





